### 2016-08-10 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Edited event times for gas burner tests & script that generates reduced data sets

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   120		  		&    114		\\
	~(3)~ 1st floor west double door opened 	&	240		  		&    245 	 	\\
	~(4)~ 2nd floor west double door opened 	&   360			  	&    354		\\
	~(5)~ 2nd floor south exterior door opened	&   480			  	&    474		\\
	~(6)~ PPV fan on 							&   600			  	&    595 		\\
	~(7)~ All burners off 						&   720 		  	&    715		\\
	~(8)~ 2nd floor east double door opened 	&   855			  	&    N/A		\\
	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 962		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage

>>>>

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   144		  		&    112		\\
	~(3)~ 1st floor west double door opened 	&	265		  		&    244 	 	\\
	~(4)~ 2nd floor west double door opened 	&   383			  	&    353		\\
	~(5)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
	~(6)~ PPV fan on 							&   624			  	&    594 		\\
	~(7)~ All burners off 						&   746 		  	&    721		\\
	~(8)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 836		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage
